\huge A Usability Evaluation of Tor Launcher

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Described conditions in S. 3.3.

@@

\section{Qualitative Testing}
\label{sec:qualitative}
We observed user behaviors to see why Tor is hard to use and interviewed users afterward to see how they felt.

\subsection{Recruitment}
We recruited people from Craigslist using an ad (Appendix~\ref{qualitative-recruitment}) and prescreening survey (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to report their age, so age calculations omit this participant's information. All of our users had at least some college education. 12 were new users and 4 had previously used Tor Browser in some capacity.

>>>>

In the first environment, E1, particular websites were blocked, which meant that they could be accessed via a default Tor configuration (i.e., bridges or proxies were not needed). In the second environment, E2, we additionally blocked the IP addresses of public Tor relays, which meant that Tor could still be accessed by enabling any of the included bridges. Finally, the third environment, E3, additionally blocked several of the included bridges, which meant experimenting with several different bridges---beyond the recommended ones---in order to successfully connect.

@@

\section{Qualitative Testing}
\label{sec:qualitative}
We observed user behaviors to identify Tor stumbling points and then interviewed them afterwards to gather explanatory data and their opinions.

\subsection{Recruitment}
We recruited people from Craigslist using an ad (Appendix~\ref{qualitative-recruitment}) and prescreening survey (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). Our age calculations omit one participant who declined to report it. All of our users had at least some college education. Twelve were new users and 4 had previously used Tor Browser in some capacity.
